Probabilities and propensities: conversion experiences in online grocery shopping

### 2017-03-22 lists_conversion_experience.rmd

---
title: "Probabilities and propensities: conversion experiences in online grocery shopping"
author: "Adrian Mackenzie"
date: "`r Sys.Date()`"
output:
tufte::tufte_handout: default
fontsize: 12pt
citation_package: biber
latex_engine: xelatex
bibliography: /home/mackenza/ref_bibs/uni.bib
bibliostyle: 'harvard'
link-citations: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

@@

```{r random-basket, echo=FALSE, cache=TRUE, fig.cap='Random basket'}
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)
csvs = list.files('data', pattern = '*.csv',full.names=TRUE)
df = bind_rows(sapply(csvs, read_tsv))
kable(sample_n(df, size=5)$name, col.names='item')
```

```{r shopping-hand}
include_graphics('figure/1_shopping.png')
```

@@

```{r  expensive-groceries, echo=FALSE, cache=TRUE, fig.margin=TRUE}
s = sample_n(df[df$price>=30,], size=10)
s$Price = s$price
s$Label = s$name
kable(s[order(s$price), c('Label','Price')], col.names=c('Item', 'Price (£)'))
```

@@

```{r arules-ex, cache=TRUE, message=FALSE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
options(digits=2)
rules<- apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=FALSE))
rules_sorted <- sort(rules, decreasing=TRUE,by="confidence")
kable(inspect(rules_sorted[1:5]))
```

The `apriori` algorithm finds sets of items that commonly occur together in transactions.  These commonly occurring sets are expressed as 'association rules.' For instance, using the `Groceries` dataset in the `R` package `arules,` we can readily see how Walmart *might* have discovered   the fabled association between diapers and beer.[^149.1] Figure \@ref(fig:arules-ex) shows how often common items appear. `Whole milk` appears most frequently.  The association rule-based model for the `Groceries` dataset illustrates some characteristic ordering practices of 1990s-style data-mining approaches to lists (the `Groceries` dataset  was acquired from a 'local German supermarket' [@Hahsler_2006a]). The association between items is expressed in the form of _rules_ not a model. These rules, a term derived from older decision support literature, define sets of associations between items. Table \@ref(tab:arules-ex) shows that the first rule has a stronger association than the second. Milk and vegetables is more likely an association than milk and buns.  A rules-based recommender system should, therefore, might put them in that order in the 'Have You Forgotten' list.

@@

```{r models}
include_graphics('figure/patel_compares_models.png')
```

>>>>

---
title: "Probabilities and propensities: conversion experiences in online grocery shopping"
author: "Adrian Mackenzie"
date: "`r Sys.Date()`"
output:
tufte::tufte_handout: default
fontsize: 12pt
citation_package: biber
latex_engine: xelatex
bibliography: /home/mackenza/ref_bibs/uni.bib
csl: "sage-harvard.csl"
link-citations: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

@@

```{r random-basket, echo=FALSE, cache=TRUE, fig.cap='Random basket'}
library(dplyr)
library(ggplot2)
library(readr)
library(knitr)
csvs = list.files('data', pattern = '*.csv',full.names=TRUE)
df = bind_rows(sapply(csvs, read_tsv))
kable(sample_n(df, size=5)$name, col.names='item', caption='A random list of Tesco grocery items')
```

```{r shopping-hand, fig.cap='A hand-written shopping list'}
include_graphics('figure/1_shopping.png')
```

@@

```{r expensive-groceries, echo=FALSE, cache=TRUE}
s = sample_n(df[df$price>=30,], size=10)
s$Price = s$price
s$Label = s$name
kable(s[order(s$price), c('Label','Price')], col.names=c('Item', 'Price (£)'), caption='Random sample of higher cost items from Tesco')
```

@@

```{r arules-ex, cache=TRUE, fig.cap='Frequency of association betwene items in the `Grocery` dataset', message=FALSE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
```

```{r arules-ex2}
options(digits=2)
rules<- apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=FALSE))
rules_sorted <- sort(rules, decreasing=TRUE,by="confidence")
kable(inspect(rules_sorted[1:5]), caption='The first five association rules for the `Groceries` dataset')
```

The `apriori` algorithm finds sets of items that commonly occur together in transactions.  These commonly occurring sets are expressed as 'association rules.' For instance, using the `Groceries` dataset in the `R` package `arules,` we can readily see how Walmart *might* have discovered   the fabled association between diapers and beer.[^149.1] Figure \@ref(fig:arules-ex) shows how often common items appear. `Whole milk` appears most frequently.  The association rule-based model for the `Groceries` dataset illustrates some characteristic ordering practices of 1990s-style data-mining approaches to lists (the `Groceries` dataset  was acquired from a 'local German supermarket' [@Hahsler_2006a]). The association between items is expressed in the form of _rules_ not a model. These rules, a term derived from older decision support literature, define sets of associations between items. Table \@ref(tab:arules-ex2) shows that the first rule has a stronger association than the second. Milk and vegetables is more likely an association than milk and buns.  A rules-based recommender system should, therefore, might put them in that order in the 'Have You Forgotten' list.

@@

```{r models, fig.cap='Precision measurements for different machine learning models'}
include_graphics('figure/patel_compares_models.png')
```
